### 2018-08-26 abstract.tex
Word hard wrap 80 col
Minor grammatical issues were implemented

Nowadays climate change pushes humankind in search new ways to generate carbon-free, reliable, nonintermittent base load power. That is reason why interest in advanced nuclear energy and, particularly \glspl{MSR} has resurged, with multiple new companies pursuing commercialization of \gls{MSR} designs\footnote{Examples include both liquid-fueled and solid-fueled molten salt designs from
Transatomic, Terrapower, Terrestrial, Moltex Energy, and Thorcon.}. To further develop these \gls{MSR} concepts researchers need tools for analyzing liquid fueled molten salt reactor depletion and fuel processing. However, most contemporary nuclear reactor physics software is unable to perform high-fidelity full-core depletion calculations in an online reprocessing regime. This paper introduces a Python script, SaltProc, which couples with the Monte Carlo code, SERPENT2, and simulates \gls{MSR} online reprocessing by modeling the changing isotopic composition of an irradiated fuel salt. SaltProc capabilities was demonstrated for full-core high-fidelity model of the commercial \gls{MSBR} concept and compared well to previous results from lower fidelity analyses.

>>>>

Today climate change pushes humankind in search new ways to generate 
carbon-free, reliable base load power. Thus,
interest in advanced nuclear energy and particularly \glspl{MSR} has resurged, 
with multiple new companies pursuing commercialization of \gls{MSR} 
designs (e.g. Transatomic, Terrapower, Terrestrial, Moltex Energy, Thorcon). To further 
develop these \gls{MSR} concepts, researchers need simulation tools for analyzing liquid 
fueled molten salt reactor depletion and fuel processing. However, most 
contemporary nuclear reactor physics software is unable to perform high-fidelity 
full-core depletion calculations in an online reprocessing regime. This paper 
introduces a Python package, SaltProc, which couples with the Monte Carlo code, 
SERPENT2, and simulates \gls{MSR} online reprocessing by modeling the changing 
isotopic composition of \gls{MSR} fuel salt. SaltProc capabilities were 
demonstrated for full-core high-fidelity model of the commercial \gls{MSBR} 
concept and compared well to previous results from lower fidelity analyses.

### 2018-08-26 introduction.tex
Minor grammatical issues were implemented

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
material moves to and from the core at specific time steps (batch) or 
continuously. In batch-wise approach the burn-up simulation stops at a given 
time and restart with a new liquid fuel composition (after removal of discarded 
materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
batch-wise approach to simulate a continuous reprocessing. ChemTriton models salt 
treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
SCALE/TRITON depletion simulation over small time steps to simulate continuous 
reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, 
jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
and current work employ a batch-wise approach.

Accounting for continuous removal or addition presents a greater challenge since it 
requires adding a term to the Bateman equations. In SCALE 
\cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of 
Bateman equations using spectrum-averaged fluxes and cross sections generated 
from a deterministic transport calculation. Approaches listed in references 
\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} 
model true continuous feeds and removals.

@@

Nuttin \emph{et al.} broke up reactor core geometry into three \gls{MCNP} cells: 
one for salt channels, one for the salt plena above and below the core and the 
last cell for the annulus, consequently, the two-region reactor core was 
approximated by one region with averaged fuel/moderator ratio 
\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This approach 
misrepresent the two-region breeder reactor concept. The unit-cell or one-region 
models may produce reliable results for homogeneous reactor cores (i.e. 
\gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs (i.e. 
\gls{MSRE}). However, a two-region \gls{MSBR} must be simulated using a whole-core 
model to capture different neutron transport characteristics in the inner and 
outer regions of the core. In particular, most fissions happens in the inner 
region while breeding occurs in the outer zone.

>>>>

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
material moves to and from the core continuously or at specific time steps 
(batch-wise). In the batch-wise approach, the burn-up simulation stops at a given 
time and restarts with a new liquid fuel composition (after removal of discarded 
materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
batch-wise approach to simulate a continuous reprocessing. ChemTriton models salt 
treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
SCALE/TRITON depletion simulation over small time steps to simulate continuous 
reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, 
jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
as well as the current work employ a batch-wise approach.

Accounting for continuous removal or addition presents a greater challenge since it 
requires adding a term to the Bateman equations. In SCALE 
\cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of 
Bateman equations using spectrum-averaged fluxes and cross sections generated 
from a deterministic transport calculation. Meanwhile, approaches listed in references 
\cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} 
model true continuous feeds and removals.

@@

Nuttin \emph{et al.} broke up reactor core geometry into three \gls{MCNP} cells: 
one for salt channels, one for the salt plena above and below the core and the 
last cell for the annulus, consequently, the two-region reactor core was 
approximated by one region with averaged fuel/moderator ratio 
\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This approach 
misrepresents the two-region breeder reactor concept. The unit-cell or one-region 
models may produce reliable results for homogeneous reactor cores (i.e. 
\gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs (i.e. 
\gls{MSRE}). However, a two-region \gls{MSBR} must be simulated using a whole-core 
model to capture different neutron transport characteristics in the inner and 
outer regions of the core. In particular, most fissions happens in the inner 
region while breeding occurs in the outer zone.

### 2018-08-26 results.tex
Minor grammatical issues were implemented

\subsection{Fuel salt composition dynamics}
The analysis of the fuel salt composition evolution provides more comprehensive 
information about the equilibrium state. Figure~\ref{fig:adens_eq} shows number 
density of major nuclides which have a strong influence on the reactor core 
physics. The concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in 
fuel salt change insignificantly after approximately 2500 days of operation. 
Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time 
interval from 16 to 20 years of operation. Hence, a quasi-equilibrium state was 
achieved after 16 years of reactor operation.
\begin{figure}[ht!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{major_isotopes_adens.png}
  \caption{Number density of major nuclides during 60 years of reactor 
  operation.}
  \label{fig:adens_eq}
\end{figure}
In contrast, a wide variety of nuclides, including fissile isotopes (e.g. 
$^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), keep accumulating 
in the core. Figure~\ref{fig:fissile_short} demonstrates production of fissile 
isotopes in the core. In the end of the considered operational time, the core 
contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
atom/b-cm). Meanwhile, the equilibrium number density of the target fissile 
isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, 
production of new fissile materials in the core as well as $^{233}$U breeding 
make it possible to compensate for negative effects of strong absorber 
accumulation and keep the reactor critical.
\begin{figure}[htp!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{fissile_short.png}
  \caption{Number density of fissile in epithermal spectrum nuclides 
  accumulation during the reactor operation.}
  \label{fig:fissile_short}
\end{figure}

@@

The effective multiplication factor of the core reduces gradually over 
operation time because the fissile material ($^{233}$U) continuously depletes 
from the fuel salt due to fission and, at the same time, fission products 
accumulates in the fuel salt.	Eventually, without fission products removal, 
the reactivity decreases to the subcritical state after approximately 500 and 
1300 days of operation for cases with no removal and volatile gases \& noble 
metals removal, respectively. The time when the simulated core reaches 
subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime. 
Therefore, removing fission products provides with significant neutronic benefit 
because allows achieve longer core lifetime.
\begin{figure}[ht!] % replace 't' with 'b' to force it to 
  \centering
  \includegraphics[width=\textwidth]{keff_rem_cases.png} 
  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} 
model with removal of various fission product groups over 10 years of 
operation.}
  \label{fig:fp_removal}
\end{figure}

>>>>

\subsection{Fuel salt composition dynamics}
The analysis of the fuel salt composition evolution provides more comprehensive 
information about the equilibrium state. Figure~\ref{fig:adens_eq} shows number 
density of major nuclides which have a strong influence on the reactor core 
physics. The concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in 
the fuel salt change insignificantly after approximately 2500 days of operation. 
Particularly, the $^{233}$U number density fluctuates less than 0.8\% in the time 
interval from 16 to 20 years of operation. Hence, a quasi-equilibrium state was 
achieved after 16 years of reactor operation.
\begin{figure}[ht!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{major_isotopes_adens.png}
  \caption{Number density of major nuclides during 60 years of reactor 
  operation.}
  \label{fig:adens_eq}
\end{figure}
In contrast, a wide variety of nuclides, including fissile isotopes (e.g. 
$^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), keep accumulating 
in the core. Figure~\ref{fig:fissile_short} demonstrates production of fissile 
isotopes in the core. In the end of the considered operational time, the core 
contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu 
($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ 
atom/b-cm). Meanwhile, the equilibrium number density of the target fissile 
isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, 
production of new fissile materials in the core as well as $^{233}$U breeding 
make it possible to compensate for negative effects of strong absorber 
accumulation and keep the reactor critical.
\begin{figure}[htp!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{fissile_short.png}
  \caption{Number density of fissile in epithermal spectrum nuclides 
  accumulation during the reactor operation.}
  \label{fig:fissile_short}
\end{figure}

@@

The effective multiplication factor of the core reduces gradually over 
operation time because the fissile material ($^{233}$U) continuously depletes 
from the fuel salt due to fission and, at the same time, fission products 
accumulates in the fuel salt.	Eventually, without fission products removal, 
the reactivity decreases to the subcritical state after approximately 500 and 
1300 days of operation for cases with no removal and volatile gases \& noble 
metals removal, respectively. The time when the simulated core reaches 
subcriticality ($k_{eff}<$1.0) for full-core model) called the core lifetime. 
Therefore, removing fission products provides with significant neutronic benefit 
and enables a longer core lifetime.
\begin{figure}[ht!] % replace 't' with 'b' to force it to 
  \centering
  \includegraphics[width=\textwidth]{keff_rem_cases.png} 
  \caption{Calculated effective multiplication factor for full-core \gls{MSBR} 
model with removal of various fission product groups over 10 years of 
operation.}
  \label{fig:fp_removal}
\end{figure}
